---
title: "demo_nih_enrollment"
output: rmarkdown::html_vignette
editor_options: 
  chunk_output_type: console
---

```{r setup}
library(codified)

# https://cran.r-project.org/web/packages/codified/vignettes/nih-enrollment-html.html#1_install_codified_package 
```

```{r load data}

```


```{r generate maping}

#### Gender mapping ####
ds_lu_gender <- tibble::tribble(
  ~input,   ~displayed            ,
  "0"   ,  "Female"               , 
  "1"   ,  "Male"                 ,
  "U"   ,  "Unknown/Not Reported"
)

knitr::kable(ds_lu_gender, caption = "Gender Mapping")

#### Race mapping ####
ds_lu_race <- tibble::tribble(
  ~input , ~displayed                                   ,
  "1"    , "American Indian/Alaska Native"              ,
  "2"    , "Asian"                                      ,
  "3"    , "Native Hawaiian or Other Pacific Islander"  ,
  "4"    , "Black or African American"                  ,
  "5"    , "White"                                      ,
  "M"    , "More than One Race"                         ,
  "6"    , "Unknown or Not Reported"
)
knitr::kable(ds_lu_race, caption = "Race Mapping")

#### Ethnicity mapping ####
ds_lu_ethnicity <- tibble::tribble(
  ~input,   ~displayed                      ,
  "2"   ,  "Not Hispanic or Latino"         ,
  "1"   ,  "Hispanic or Latino"             ,
  "0"   ,  "Unknown/Not Reported Ethnicity"
)
knitr::kable(ds_lu_ethnicity, caption = "Ethnicity Mapping")
```

```{r apply maps to dataset}
#### counts for each subgroup ####
ds_summary_long <- codified::table_nih_enrollment(
  d              = ds,
  d_lu_gender    = ds_lu_gender,
  d_lu_race      = ds_lu_race,
  d_lu_ethnicity = ds_lu_ethnicity
)

knitr::kable(ds_summary_long, caption = "Counts of Each Subgroup")

#### conform to NIH cosmetics ####
codified::table_nih_enrollment_pretty(
  d              = ds,
  d_lu_gender    = ds_lu_gender,
  d_lu_race      = ds_lu_race,
  d_lu_ethnicity = ds_lu_ethnicity
)
